Adaptive Video Streaming System with PID-Based Quality Control and Optimized Bitstream Extraction

### 2015-02-04 tmm.tex
readable version for TMM

% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Scalable Video Streaming with PID-Based Quality Control and Optimized Bitstream Extraction}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be scalable, i.e., of flexible bitrate and adaptive video quality. This paper gives solutions for two key problems within such a scalable video streaming system. We first propose a quality control algorithm, which allows the video streaming system to adjust its video quality along with the real bandwidth change. The algorithm is based on the Proportional-Integral-Derivative (PID) control method and can deliver best video quality with least quality fluctuation. Then for streaming systems that adopt Scalable Video Coding (SVC), we present an efficient solution for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole bitstream under given bitrate constraint. This solution features a linear error model, which is utilized to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme, which assigns each data packet a priority value to use for the R-D optimized extraction. Experimental results show that our quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to the extractors of JSVM, without computational complexity increment. The quality control algorithm has also been implemented in online video website www.7dlive.com and turns out to be practically effective in applications.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
\IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet. Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, and so on. In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted. Among other features, video streaming makes it easy to watch video anywhere and anytime, and is an increasingly important way for people to consume video content.

One of the biggest challenge for video streaming is the variety of users' network environment. The users may use various types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch to a different one on going (e.g., from Wi-Fi to cellular network). Even in the same network, a user's available bandwidth may change from time to time, influenced by the overall traffic. During such an environment, bandwidth fluctuation is inevitable. If the video is streamed at a constant bitrate, it would be difficult or impossible for the client to keep a non-paused smooth playing. Therefore, to achieve better watching experience for users with various network environments, we should be able to adjust the video's bitrate or quality according to the bandwidth change. In other words, the video streaming system needs to be scalable.

There are two options to enable scalable video streaming. The first option is called simulcast, where several independent bitstreams are stored at the server side, and the client selects one of them according to its current bandwidth. Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by MPEG, mostly uses this option. Simulcast systems like DASH can provide some scalability and is relatively easy to deploy. However, the scalability it provides is limited to the number of streams, and the processing and storage of multiple streams significantly increase time and space cost. On the contrary, the second option, which is to adopt Scalable Video Coding (SVC) \cite{SVC}, does not have above shortcomings. Compared to simulcast, SVC provides seamless scalability and higher coding efficiency, thus is a better choice to build a scalable video streaming system. While our work in this paper can be partly adapted to the simulcast system, we will mainly focus on the second option, i.e., SVC streaming system.

The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}, which has provided an effective way to deal with the new challenges of modern video applications. SVC allows efficient scalability in terms of video frame rate, spatial resolution, and picture fidelity, with only one single bitstream. The SVC bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and several enhancement layers for video quality improvement. By discarding NALUs of the enhancement layers, the bitstream can be extracted as required, providing the most appropriate data rate and video service according to the client capability and network conditions.

In SVC streaming system, there are two important issues that need to be addressed. First is quality control, and the second is bitstream extraction. Quality control means controlling the video quality (as well as the bitrate) to follow the change of bandwidth. Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth. Given this bitrate, how to extract from the whole SVC stream to form a optimal sub-stream becomes the bitstream extraction problem. Optimized bitstream extraction aims to select a subset of data which represents video with best quality, or minimal distortion, under the constrain of given bitrate. It should be noted that, bitstream extraction is not only useful in scalable video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.

In this paper, we propose novel solutions for these two issues and construct an efficient scalable video streaming system. Apple Darwin Streaming Server (DSS) \cite{DSS}, which has been widely used to collect, cache, schedule and transmit multimedia contents in practice, is chosen as the basis of the system. We modified the original DSS project and added SVC support to it, for the purpose of both research and application. A new quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation. In this algorithm, we can monitor and even predict the relationship between the network bandwidth and the current video data rate, so that quality adjustment can be made at any time and to any extent, accurately and smoothly. For the bitstream extraction problem, we propose a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. The linear error model exploits the linear feature of H.264/AVC coding process and achieves good performance in distortion estimation. Using this model, the error caused by the removal of each enhancement packet can be obtained independently. This enables us to estimate the distortion caused by discarding any combination of packets. Based on that, we design a greedy algorithm to calculate the priority of each quality enhancement packet according to its R-D impact. The priority value of packets can be stored in the bitstream and used for optimized extraction. The proposed algorithms perform well in experiments and the quality control algorithm is also used in practical streaming systems and proved quite effective.

@@

In this section, we analyze the two most concerned problems in SVC streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.

@@

In \cite{Amonou07}, Amonou et al. proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}. This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM. In Amonou's framework, a Quality Layer value, which reflects a packet's rate-distortion (R-D) impact, is calculated and used for R-D optimized bitstream extraction. The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved. So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy. Sun \cite{Sun09} and Maani \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames. Sun's method is almost as good as JSVM for the performance, but with a much reduced complexity. Maani's model can achieve better estimation accuracy than JSVM; however, in order to get robust and accurate model parameters, more computation is needed for training.

In our previous work \cite{Zhang12}, we noticed the mismatch between quadratic calculations in distortion criteria like MSE or PSNR and the essential linear operations in the coding process, and proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. The linear error model exploits the linear feature of pixel value errors and achieves good performance in distortion estimation and bitstream extraction with reference. However, this work assumes that the original sequence is available for reference, which is not always true. It needs adaption for widespread application.

The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical scalable video streaming system.

@@

As an effective and flexible control technique, PID control has been used to solve all kinds of control problems. In the area of video coding, we notice that PID is utilized to design rate control algorithms by many papers. For instance, in \cite{Wong04} a PID-based real time rate control scheme is proposed to trade-off between spatial and temporal quality and smooth the video quality between frames; in \cite{Yang10}, the authors designed an incremental rate control algorithm for H.264/SVC, in which the PID method is used to provide robust buffer control for each layer. We also notice some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept. However, we have not found any paper that integrates PID method into the quality control of video streaming. While rate control of video coding and quality control of video streaming are two different problems, they do share some common properties, such as the buffer mechanism and the requirement for smoothness. That inspires us to design a PID-based quality control algorithm and utilize it to deliver best video quality with least quality fluctuation.

In this section, we first introduce the \textit{quality level} concept to discretization the bitrate and quality of scalable video. Then we define the process variable used in our PID-based quality control algorithm. After that, the PID-based quality control algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.

@@

The video bitrate or quality is a continuous value. In practical operation, it is not possible to control it at an arbitrary precision. So we propose a \textit{quality level} concept as the discrete description of the video quality. When the video quality needs to be adjusted, we simply increase or decrease the quality level. Each quality level corresponds to a certain bitrate. A Higher quality level corresponds to a higher bitrate, vice versa. The number of quality levels and how they are mapped to sub-streams with different bitrates depends on requirement or implementation. The more quality levels are defined, the more precisely the control algorithm can adjust bitrate to follow the bandwidth change.

@@

For DSS, two timelines are important. Push timeline indicates the time of pushing video data packets to streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet. Their relationship is shown in Fig. \ref{fig:intervals}. The program will check the timelines periodically, and, in the default quality control algorithm of DSS, use the packet delays to decide whether quality change is needed. The two intervals shown in Fig. \ref{fig:intervals}, i.e., check interval and actual interval, are worth notice and may provide useful information. In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to that check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}. If \textit{actual\_interval} is smaller than \textit{check\_interval}, it means that less data is pushed to the client, and the pushing is slowed down because bandwidth is relatively low at this time. On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the bandwidth condition is good and data is being pushed quickly to the client. The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the data rate appropriate for bandwidth and the current pushing data rate.

@@

\begin{figure}[t]
\centering
\includegraphics[width = 0.9\linewidth]{intervals.jpg}
\caption{Push Time and Play Time \label{fig:intervals}}
\end{figure}

@@

 \begin{figure}[h]
 \centering
 \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
 \caption{SVC GOP structure \label{fig:GOP_Structure}}
 \end{figure}

@@

In this paper, we propose a scalable video streaming system with PID-based quality control algorithm and optimized bitstream extraction. The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change. Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction. The bitstream extraction method we propose includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet. The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction. Experimental results show that the proposed method can achieve PSNR gain of up to 0.5 compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.

The PID-based quality control algorithm of this paper has already been integrated into the online scalable video streaming website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation. This algorithm can also be easily used in other streaming systems, e.g., DASH systems. For the bitstream extraction method, there is future work to be done in the following two directions. First, we strive to integrate the bitstream extraction method into DSS, and combine it with the PID-based quality control to give user adaptive video streaming with best watching experience. Second, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension.

@@

@@

\bibitem{Schierl10}
Y. Schierl, R. Sanchez, C. Globisch, Hellge, and T. Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', in {\em Multimedia Tools And Applications}, vol. 55, no.2, pp. 227-246, Sep. 2010.

>>>>

% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Adaptive Video Streaming System with PID-Based Quality Control and Optimized Bitstream Extraction}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In order to meet the challenge brought by bandwidth fluctuation of the user's network, modern video streaming systems tend to be adaptive, i.e., able to adjust the video quality according to available bandwidth. This paper implements such an adaptive video streaming system which utilizes the Scalable Video Coding (SVC) technology, and gives novel solutions for two key problems within the system. First, a quality control algorithm is proposed for the video streaming system to adjust its video quality along with the real bandwidth change. The algorithm is based on the Proportional-Integral-Derivative (PID) control method and designed to deliver best video quality with least quality fluctuation. Second, an efficient solution is present for the bitstream extraction problem, which aims to select an optimal sub-stream from the whole SVC video bitstream under given bitrate constraint. The solution features a linear error model to estimate the distortion caused by discarding any combination of data packets, and a greedy algorithm scheme to assign each data packet a priority value for Rate-Distortion optimized extraction. Experimental results show that the PID-based quality control algorithm can drastically reduce the quality fluctuation while still keeping a high quality level, and the bitstream extraction method can achieve a significant PSNR gain compared to existing reference extractors, without computational complexity increment. The system is currently running at the online video website www.7dlive.com and proves to be practically effective.
\end{abstract}

@@

\section{Introduction}
\label{sec:intro}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
\IEEEPARstart{V}{ideo} streaming applications are becoming more and more popular on the Internet. Examples of the most common usage scenarios include VOD (Video On Demand), live broadcasting, video-based online education, etc. In these applications, video data is constantly delivered to different clients over various transmission channels, and the client media player can begin playing the video before the entire file has been transmitted. Among other features, video streaming makes it easy to watch video anywhere and anytime, and is an increasingly important way for people to consume video content.

One of the biggest challenge for video streaming is the variety of users' network environment. A user may use different types of network (Ethernet, Wi-Fi, Cellular, etc) and may also switch from one type to another (e.g., from Wi-Fi to cellular network) on going. Even in the same network, the user's bandwidth may change from time to time, influenced by the overall traffic. During such an environment, bandwidth fluctuation is inevitable. If the video is streamed at a constant bitrate, it would be difficult or impossible for the client to keep a non-paused smooth playing. Therefore, to achieve better watching experience for users with various network environment, the video's bitrate or quality should be able to adjust according to the bandwidth change. In other words, the video streaming system needs to be adaptive.

There are generally two options to enable adaptive video streaming. The first option is called simulcast, where several independent bitstreams with different video quality are stored at the server, and the client selects one of them according to currently available bandwidth. Dynamic Adaptive Streaming over HTTP (DASH) \cite{DASH}, which is standardized by the Moving Picture Expert Group (MPEG), belongs to this option. The second option is to adopt the Scalable Video Coding (SVC) \cite{SVC} technology, which allows efficient scalability of video bitrate and quality with only one single bitstream. The generally-known term SVC usually refers to the scalable extension of the H.264/AVC video coding standard \cite{SVCOverview}. In SVC, a video bitstream is composed of Network Abstract Layer Units (NALUs), which are separated into multiple layers: one base layer for basic video quality and multiple enhancement layers for video quality improvement. By discarding NALUs of the enhancement layers, the bitstream can be extracted to provide the most appropriate data rate and video quality as required.

The advantage of simulcast systems is that they need little modification of existing infrastructure and therefore are easy to deploy. Most commercial video websites, YouTube \cite{YouTube} for instance, use this option to enable quality adaptation. However, the adaptive range and granularity simulcast provides is strictly limited to the number of streams (YouTube videos have 5 quality levels at most: 240p, 360p, 480p, 720p and 1080p), and the processing and storage of multiple video streams significantly increase time and space cost. SVC streaming systems, on the contrary, do not have above shortcomings. An SVC video bitstream can be extracted at the granularity of one NALU (a very small partition of data), and thus can provide seamless scalability and adaptation. Besides, performance analysis \cite{SVCPerformance} shows that SVC also has much higher coding efficiency than simulcast, despite some computation and bitrate overhead comparing with single layer stream. Therefore, SVC is considered to be a better choice for adaptive video streaming systems. While our work in this paper can be partly used in a simulcast system, we will mainly focus on building an adaptive streaming system using SVC.

To guarantee good performance of SVC streaming system, there are two important issues that need to be addressed well. First is quality control, and the second is bitstream extraction. Quality control means controlling the video quality (as well as the bitrate) to follow the change of bandwidth. Once the bandwidth has changed, the quality control algorithm should determine a bitrate suitable for the current bandwidth. Given this bitrate, how to extract data from the whole SVC stream to form an optimal sub-stream becomes the bitstream extraction problem. Optimized bitstream extraction aims to select a subset of NALUs (or packets) which represents video with best quality, or minimal distortion, under the constrain of the given bitrate. It should be noted that, bitstream extraction is not only useful in adaptive video streaming, but also in other SVC application scenarios where part of data needs to be obtained or kept, e.g., the archiving of surveillance video.

In this paper, we propose novel solutions for these two issues and construct an efficient adaptive video streaming system. Apple Darwin Streaming Server (DSS) \cite{DSS}, which has been widely used to collect, cache, schedule and transmit multimedia contents in practice, is chosen as the basis of the system. We modified the original DSS project and added SVC support to it, for the purpose of both research and application. A new quality control algorithm based on the Proportional-Integral-Derivative (PID) control concept is proposed to replace the native one in DSS, and achieves higher average quality level with less quality fluctuation. For the bitstream extraction problem, we propose a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. This model enables us to accurately estimate the distortion caused by discarding any combination of packets. Based on that, we design a greedy algorithm to assign priority for each quality enhancement packet according to its rate-distortion (R-D) impact. The priority value of each packet can be stored in the bitstream and used for optimized extraction. The proposed algorithms perform well in experiments and the quality control algorithm is also implemented in the practical streaming system we construct and proved quite effective.

@@

In this section, we analyze the two most concerned problems in SVC adaptive streaming, i.e., quality control and bitstream extraction, and introduce some existing related works on them.

@@

In \cite{Amonou07}, Amonou et al. proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}. This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM. In Amonou's framework, a Quality Layer value, which reflects a packet's R-D impact, is calculated and used for R-D optimized bitstream extraction. The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved. So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy. Sun et al. \cite{Sun09} and Maani et al. \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames. Sun et al.'s method is almost as good as JSVM in regard of performance, but has much reduced complexity. Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is  a training-based model, more computation is needed to get robust model parameters.

In our previous work \cite{Zhang12}, we noticed the mismatch between quadratic calculations in distortion criteria like MSE or PSNR and the essential linear operations in the coding process, and proposed a linear error model to directly estimate pixel value errors before MSE or PSNR is calculated. The linear error model exploits the linear feature of pixel value errors and achieves good performance in distortion estimation and bitstream extraction with reference. However, this work assumes that the original video sequence is available for reference, which is not always true. Adaptation to handle the special characteristic of the no-reference case is lacking, and is included in this paper.

The following of this paper will present solutions for the above problems, and lay a solid foundation for a practical adaptive video streaming system.

@@

As an effective and flexible control technique, PID control has been used to solve all kinds of control problems. In the area of video coding, we notice that PID is utilized to design rate control algorithms by many papers. For instance, in \cite{Wong04} a PID-based real time rate control scheme is proposed to trade-off between spatial and temporal quality and smooth the video quality between frames; in \cite{Yang10}, the authors designed an incremental rate control algorithm for H.264/SVC, in which the PID method is used to provide robust buffer control for each layer. We also notice that some researchers have proposed theoretical model or middle-ware framework for QoS adaptation \cite{Li98}\cite{Li99}, with PID as the basic control concept. However, we have not found any paper that integrates PID method into the quality control of video streaming. While rate control of video coding and quality control of video streaming are two different problems, they do share some common properties, such as the buffer mechanism and the requirement for smoothness. That inspires us to design a PID-based quality control algorithm and utilize it to deliver best video quality with least quality fluctuation.

In this section, we first introduce the \textit{quality level} concept to discretization the bitrate and quality of scalable video. Then we define the process variable used in our PID-based quality control algorithm. After that, the algorithm is formulated and explained in detail, followed by the brief discussion of parameter selection.

@@

The video quality is a continuous value. In practical operation, it is not possible to control it at an arbitrary precision. So we propose a \textit{quality level} concept as the discrete description of the video quality. When the video quality needs to be adjusted, we simply increase or decrease the quality level. Each quality level corresponds to a certain bitrate. A higher quality level corresponds to a higher bitrate and vice versa. The number of quality levels and how they are mapped to sub-streams with different bitrates depends on actual requirement or implementation. The more quality levels are defined, the more precisely the control algorithm can adjust bitrate to follow the bandwidth change. As pointed out in section \ref{sec:intro}, simulcast streaming systems can only have limited quality levels while SVC streaming systems can define quality levels at a much finer granularity.

@@

In DSS, two timelines are important. Push timeline indicates the time of pushing video data packets to streaming buffer, and play timeline indicates the time these data packet should be played, i.e., the presentation time stamp (often seen as PTS) of each packet. Their relationship is shown in Fig. \ref{fig:intervals}. The program will check the timelines periodically, and, in the default quality control algorithm of DSS, use the packet delays to decide whether quality change is needed. The two intervals shown in Fig. \ref{fig:intervals}, i.e., check interval and actual interval, are worth notice and may provide useful information. In the ideal situation, during each check interval, the server pushes an amount of data that will actually play for a period of time equal to that check interval, i.e., \textit{actual\_interval} = \textit{check\_interval}. If \textit{actual\_interval} is smaller than \textit{check\_interval}, it means that less data is pushed to the client, and the pushing is slowed down because bandwidth is relatively low at this time. On the other hand, if \textit{actual\_interval} is larger than \textit{check\_interval}, it indicates the bandwidth condition is good and data is being pushed quickly to the client. The ratio of these two intervals, i.e., \textit{actual\_check interval ratio}, is in direct proportion to the ratio of the data rate appropriate for bandwidth and the current pushing data rate.

@@

\begin{figure}[t]
\centering
\includegraphics[width = 0.9\linewidth]{intervals.jpg}
\caption{Two timelines in Darwin Streaming Sever (DSS) \label{fig:intervals}}
\end{figure}

@@

 \begin{figure}[h]
 \centering
 \includegraphics[width = 0.9\linewidth]{GOPStructure.jpg}
 \caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
 \end{figure}

@@

In this paper, we propose an adaptive video streaming system with PID-based quality control algorithm and optimized bitstream extraction. The PID-based quality control algorithm has a flexible mechanism to determine the suitable quality level so that it gives an accurate and swift response to the bandwidth change. Comparing with the original algorithm in DSS, this algorithm has reduced quality fluctuation significantly to improve audience satisfaction. The bitstream extraction method we propose includes a linear error model to estimate the distortion caused by discarding any combination of packets and a greedy algorithm to assign priority to each data packet. The packets' priority values can then be stored in the bitstream and used for R-D optimized extraction. Experimental results show that the proposed method can achieve PSNR gain of up to 0.5 compared to the JSVM QL extractor under the same bitrate constrain, also with the same computational complexity.

The PID-based quality control algorithm of this paper has already been integrated into the online website www.7dlive.com and performs well in automatically adapting to the user's bandwidth fluctuation. This algorithm can also be easily used in other streaming systems, e.g., DASH systems. For the bitstream extraction method, there is future work to be done in the following two directions. First, we strive to integrate the bitstream extraction method into DSS, and combine it with the PID-based quality control to give user adaptive video streaming with best watching experience. Second, since the next generation video coding standard High Efficiency Video Coding (HEVC) \cite{HEVC} adopts the similar coding framework as its predecessor H.264/AVC, we expect to apply this paper's model and approach to the emerging HEVC standard and its scalable extension.

@@

\bibitem{YouTube}
https://www.youtube.com/

\bibitem{SVCPerformance}
M. Wien , H. Schwarz and T. Oelbaum,  ``Performance Analysis of SVC'',  in {\em IEEE Trans. Circuits Syst. Video Technol.}, vol. 17, no. 9, pp.1194-1203. Sep. 2007.

@@

\bibitem{Schierl10}
Y. Schierl, R. Sanchez, C. Globisch, Hellge, and T. Wiegand, ``Priority-based media delivery using SVC with RTP and HTTP streaming'', in {\em Multimedia Tools And Applications}, vol. 55, no. 2, pp. 227-246, Sep. 2010.
